k-Space Domain Parallel Transmit Pulse Design

### 2020-09-10 Manuscript/kPtx_paper.tex
wag brought bib into main doc

\documentclass[11pt]{article}
% Command line: pdflatex -shell-escape compulse.tex
\usepackage{geometry} 
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{booktabs}
\usepackage{times}
\usepackage{bm}
\usepackage{fixltx2e}
\usepackage[outerbars]{changebar}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{color}
\usepackage{tabularx}
\usepackage{ulem}
\usepackage{verbatim}
\usepackage{textcomp}

@@

\usepackage[noend]{algpseudocode}

@@

\usepackage{todonotes}

\graphicspath{{Figure/}}

@@

\bibliographystyle{cse}  % cse doesn't work
\bibliography{kPtx_paper}

>>>>

\documentclass[11pt]{article}
% Command line: pdflatex -shell-escape compulse.tex
\usepackage{geometry} 
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{booktabs}
\usepackage{times}
\usepackage{bm}
\usepackage{fixltx2e}
\usepackage[outerbars]{changebar}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{color}
\usepackage{tabularx}
\usepackage{ulem}
%\usepackage{verbatim}
\usepackage{textcomp}
\usepackage{hyperref}
\hypersetup{colorlinks=false,urlcolor=blue,linkcolor=blue}
\usepackage{caption}

@@

%\usepackage[noend]{algpseudocode}

@@

%\usepackage{todonotes}

%\graphicspath{{Figure/}}

@@

\bibliographystyle{cse}
%\bibliography{kPtx_paper}

\begin{thebibliography}{10}
\providecommand{\url}[1]{\texttt{#1}}
\providecommand{\urlprefix}{URL }

\bibitem{Katscher:2003:Magn-Reson-Med:12509830}
Katscher U, B{\"o}rnert P, Leussler C, van~den Brink JS.
\newblock Transmit {SENSE}.
\newblock Magn Reson Med 2003;\hspace{0pt}49:144--150.

\bibitem{zhu2004parallel}
Zhu Y.
\newblock Parallel excitation with an array of transmit coils.
\newblock Magn Reson Med 2004;\hspace{0pt}51:775--784.

\bibitem{malik:mrm:2015}
Malik SJ, Hajnal JV.
\newblock Phase relaxed localized excitation pulses for inner volume fast spin
  echo imaging.
\newblock Magn Reson Med 2016;\hspace{0pt}76:848--861.

\bibitem{mooiweer:2016}
Mooiweer R, Sbrizzi A, Raaijmakers AJE, Van~den Berg CAT, Luijten PR, Hoogduin
  H.
\newblock Combining a reduced field of excitation with {SENSE}-based parallel
  imaging for maximum imaging efficiency.
\newblock Magn Reson Med 2016;\hspace{0pt}78:88--96.

\bibitem{Zhang:2007:Magn-Reson-Med:16526012}
Zhang Z, Yip CY, Grissom W, Noll DC, Boada FE, Stenger VA.
\newblock Reduction of transmitter {B1} inhomogeneity with transmit {SENSE}
  slice-select pulses.
\newblock Magn Reson Med 2007;\hspace{0pt}57:842--847.

\bibitem{cloos:kpstd:2012}
Cloos MA, Boulant N, Luong M, Ferrand G, Giacomini E, Le~Bihan D, Amadon A.
\newblock {$k_T$}-{Points}: {Short} three-dimensional tailored {RF} pulses for
  flip-angle homogenization over an extended volume.
\newblock Magn Reson Med 2011;\hspace{0pt}67:72--80.

\bibitem{deng:2009}
Deng W, Yang C, Alagappan V, Wald LL, Boada FE, Stenger VA.
\newblock Simultaneous z-shim method for reducing susceptibility artifacts with
  multiple transmitters.
\newblock Magn Reson Med 2009;\hspace{0pt}61:255--259.

\bibitem{Grissom:2006:MRM}
Grissom WA, Yip CY, Zhang Z, Stenger VA, Fessler JA, Noll DC.
\newblock Spatial domain method for the design of {RF} pulses in multicoil
  parallel excitation.
\newblock Magn Reson Med 2006;\hspace{0pt}56:620--9.

\bibitem{malik2012tailored}
Malik SJ, Keihaninejad S, Hammers A, Hajnal JV.
\newblock Tailored excitation in {3D} with spiral nonselective {(SPINS) RF}
  pulses.
\newblock Magn Reson Med 2012;\hspace{0pt}67:1303--1315.

\bibitem{davids2016fast}
Davids M, Schad LR, Wald LL, Guerin B.
\newblock Fast three-dimensional inner volume excitations using parallel
  transmission and optimized k-space trajectories.
\newblock Magn Reson Med 2016;\hspace{0pt}76:1170--1182.

\bibitem{orzada:2019}
Orzada S, Solbach K, Gratz M, Brunheim S, Fiedler TM, Johst S, Bitz AK,
  Shooshtary S, Abuelhaija A, Voelker MN, Rietsch SHG, Kraff O, Maderwald S,
  Fl\"oser M, Oehmigen M, Quick HH, Ladd ME.
\newblock A 32-channel parallel transmit system add-on for 7t mri.
\newblock PLOS ONE 2019;\hspace{0pt}14:1--20.

\bibitem{deng:2011}
Deng W, Yang C, Stenger VA.
\newblock Accelerated multidimensional radiofrequency pulse design for parallel
  transmission using concurrent computation on multiple graphics processing
  units.
\newblock Magn Reson Med 2011;\hspace{0pt}65:363--369.

\bibitem{setsompop2008magnitude}
Setsompop K, Wald L, Alagappan V, Gagoski B, Adalsteinsson E.
\newblock Magnitude least squares optimization for parallel radio frequency
  excitation design demonstrated at 7 {Tesla} with eight channels.
\newblock Magn Reson Med 2008;\hspace{0pt}59:908--915.

\bibitem{brunner2010optimal}
Brunner DO, Pruessmann KP.
\newblock Optimal design of multiple-channel {RF} pulses under strict power and
  {SAR} constraints.
\newblock Magn Reson Med 2010;\hspace{0pt}63:1280--1291.

\bibitem{hoyos:tmi:2014}
Hoyos-Idrobo A, Weiss P, Massire A, Amadon A, Boulant N.
\newblock On variant strategies to solve the magnitude least squares
  optimization problem in parallel transmission pulse design under strict {SAR}
  and power constraints.
\newblock IEEE Trans Med Imag 2014;\hspace{0pt}33:739--748.

\bibitem{fessler2005toeplitz}
Fessler JA, Lee S, Olafsson VT, Shi HR, Noll DC.
\newblock Toeplitz-based iterative image reconstruction for {MRI} with
  correction for magnetic field inhomogeneity.
\newblock IEEE Trans Sig Proc 2005;\hspace{0pt}53:3393--3402.

\bibitem{grissom:ismrm18}
Grissom WA.
\newblock {k-Space} domain parallel transmit pulse design.
\newblock In Proceedings 26th Scientific Meeting, International Society for
  Magnetic Resonance in Medicine, Paris. 2018;\hspace{0pt} p. 3396.

\bibitem{luo2019grappa}
Luo T, Noll DC, Fessler JA, Nielsen JF.
\newblock A {GRAPPA} algorithm for arbitrary {2D/3D} non-{Cartesian} sampling
  trajectories with rapid calibration.
\newblock Magn Reson Med 2019;\hspace{0pt}82:1101--1112.

\bibitem{lustig2008fast}
Lustig M, Kim SJ, Pauly JM.
\newblock A fast method for designing time-optimal gradient waveforms for
  arbitrary k-space trajectories.
\newblock {IEEE} Trans Med Imag 2008;\hspace{0pt}27:866--873.

\bibitem{Fessler:2003fk}
Fessler JA, Sutton BP.
\newblock Nonuniform fast {Fourier} transforms using min-max interpolation.
\newblock IEEE Trans Sig Proc 2003;\hspace{0pt}51:560--574.

\bibitem{stenger2000three}
Stenger VA, Boada FE, Noll DC.
\newblock Three-dimensional tailored {RF} pulses for the reduction of
  susceptibility artifacts in {$T_2^*$}-weighted functional {MRI}.
\newblock Magn Reson Med 2000;\hspace{0pt}44:525--531.

\bibitem{yang2010four}
Yang C, Deng W, Alagappan V, Wald LL, Stenger VA.
\newblock Four-dimensional spectral-spatial {RF} pulses for simultaneous
  correction of {B1+} inhomogeneity and susceptibility artifacts in
  {T2*}-weighted {MRI}.
\newblock Magn Reson Med 2010;\hspace{0pt}64:1--8.

\end{thebibliography}
